Constraining tensorial and scalar couplings with $B\to K\bar\mu\mu$ and $B_s\to \bar\mu\mu$

### 2014-12-11 tensor/draft/draft-tensor-op.tex
[draft-tensor-op] added figures for the SM-EFT scenario

Both observables exihibit strong suppression factors for vectorial and dipole
couplings present in the SM, thereby enhancing their sensitivity to tensorial and
scalar couplings \cite{Bobeth:2007dw, Bobeth:2012vn}. A similar enhancement of
scalar couplings compared to helicity-suppressed vectorial couplings of the SM 
is well-known from $B_s\to \bar\mu\mu$. Unfortunately the limited data set of
$B\to K^*(\to K\pi) \bar\ell\ell$ from LHCb \cite{Aaij:2013qta} still does not
allow to perform current angular analysis without the assumption of vanishing
scalar and tensorial couplings in this decay mode. In the future also certain
angular observables in $B\to K^* \bar\ell\ell$ will provide additional constraints
on such couplings, as for example $J_{6c}$ \cite{Altmannshofer:2008dz}
and the linear combinations $(J_{1s} - 3 J_{2s})$ and $(J_{1c} + J_{2c})$ 
\cite{Matias:2012xw, Bobeth:2012vn} as well as at low recoil the experimental
test of the relations $H_T^{(2)} = H_T^{(3)}$ and $J_7 = 0$ \cite{Bobeth:2012vn}.

@@

\begin{figure*}
  \includegraphics[width=.325\textwidth]{plots/pdf/res-SSp.pdf}
%  \includegraphics[width=.32\textwidth]{plots/pdf/res-PPp.pdf}
  \includegraphics[width=.325\textwidth]{plots/pdf/res-SPplus.pdf}
  \includegraphics[width=.325\textwidth]{plots/pdf/res-SPminus.pdf}
  \caption{
    \eos{
    Constraints on real-valued scalar couplings $\wilson{S,\,S',\,P,\,P'}$ 
    from only $F_H^\mu$~(blue), only $\overline{\cal B}(B_s \to \bar\mu\mu)$ (green) 
    and their combination with other data in \reftab{tab:observables} as well as
    $\wilson{10} \in [-1,\, 9]$, $\wilson{10'} \in [-5,\,5]$ (red) 
    at 68\% (darker) and 95\% (lighter) probability. The constraints on 
    $(\wilson{P}Ê\pm \wilson{P'})$ are identical to $(\wilson{S}Ê\pm \wilson{S'})$
    [left], apart from a small shift of the contours by $(+0.2,\, 0.15)$.
    }
  }
  \label{fig:scalar}
\end{figure*}

@@

@@

%
%
%
%--------+---------+---------+---------+---------+---------+---------+---------+
\section{
  Standard model predictions
  \label{app:SM:predictions}
}

>>>>

Both observables exihibit strong suppression factors for vectorial and dipole
couplings present in the SM, thereby enhancing their sensitivity to tensorial and
scalar couplings \cite{Bobeth:2007dw, Bobeth:2012vn}. A similar enhancement of
scalar couplings compared to helicity-suppressed vectorial couplings of the SM 
is well-known from $B_s\to \bar\mu\mu$. Unfortunately the limited data set of
$B\to K^*(\to K\pi) \bar\ell\ell$ from LHCb \cite{Aaij:2013qta} still does not
allow to perform current angular analysis without the assumption of vanishing
scalar and tensorial couplings in this decay mode. In the future also certain
angular observables in $B\to K^* \bar\ell\ell$ will provide additional constraints
on such couplings, as for example $J_{6c}$ \cite{Altmannshofer:2008dz}
and the linear combinations $(J_{1s} - 3 J_{2s})$ and $(J_{1c} + J_{2c})$ 
\cite{Matias:2012xw, Bobeth:2012vn} as well as at low recoil the experimental
test of the relations $H_T^{(2)} = H_T^{(3)}$ and $J_7 = 0$~\cite{Bobeth:2012vn}.

@@

\begin{figure*}
  \includegraphics[width=.325\textwidth]{plots/pdf/res-SSp.pdf}
%  \includegraphics[width=.32\textwidth]{plots/pdf/res-PPp.pdf}
  \includegraphics[width=.325\textwidth]{plots/pdf/res-SPplus.pdf}
  \includegraphics[width=.325\textwidth]{plots/pdf/res-SPminus.pdf}
  \caption{
    \eos{
    Constraints on real-valued scalar couplings $\wilson{S,\,S',\,P,\,P'}$ 
    from only $F_H^\mu$~(blue), only $\overline{\cal B}(B_s \to \bar\mu\mu)$ (green) 
    and their combination with other data in \reftab{tab:observables} as well as
    $\wilson[NP]{10} \in [-1,\, 9]$, $\wilson[NP]{10'} \in [-5,\,5]$ (red) 
    at 68\% (darker) and 95\% (lighter) probability. The constraints on 
    $(\wilson{P}Ê\pm \wilson{P'})$ are identical to $(\wilson{S}Ê\pm \wilson{S'})$
    [left], apart from a small shift of the contours by $(+0.2,\, 0.15)$.
    }
  }
  \label{fig:scalar}
\end{figure*}

@@

\begin{figure*}
  \includegraphics[width=.35\textwidth]{plots/pdf/res-real_SSp_constr.pdf}
  \includegraphics[width=.35\textwidth]{plots/pdf/res-cmplx_SSp_constr.pdf}
  \caption{
    \eos{
    Constraints on real-valued [left] and complex-valued [right] scalar couplings 
    $\wilson{S,\,S'}$ in the scenario SM-EFT from only $\overline{\cal B}(B_s \to 
    \bar\mu\mu)$ (blue) and 
    all data in \reftab{tab:observables} (green) marginalising over non-zero 
    $\mbox{Re}(\wilson[NP]{10}) \in [-1,\, 9]$ as well as and 
    $\mbox{Im}(\wilson[NP]{10})$ and $\mbox{Re, Im}(\wilson[NP]{10'}) \in [-5,\,5]$, 
    or all data but $\mbox{Re, Im}(\wilson[NP]{10,\, 10'}) = 0$ (red)
    at 68\% (darker) and 95\% (lighter) probability. 
    }
  }
  \label{fig:scalar:SM-EFT}
\end{figure*}

@@

%
%
%
%--------+---------+---------+---------+---------+---------+---------+---------+
%\section{
%  Standard model predictions
%  \label{app:SM:predictions}
%}
